Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-20 cav2017/cav2017.tex
changed name of 2nd cegis approach to multi-staged verification approach

\caption{The CEGIS loop with abstraction refinement\label{fig:CEGARIS}.}

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{CEGIS with incremental precision, completeness threshold and sampling rate}
\label{sec:CEGIS-precision-incrementation}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

 \end{tikzpicture}
}}
\caption{The CEGIS loop with incremental precision, 
completeness threshold and sampling rate.}
\label{fig:CEGIS-precision-increment}
\end{figure}

>>>>

\caption{CEGIS with abstraction refinement\label{fig:CEGARIS}.}

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{CEGIS with multi-staged verification phase}
\label{sec:CEGIS-precision-incrementation}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

 \end{tikzpicture}
}}
\caption{CEGIS with multi-staged verification phase.}
\label{fig:CEGIS-precision-increment}
\end{figure}
